Distributional State Aggregation

### 2020-03-09 minutia/paper/paper.tex
IQR  in progress
Paper updated befor the meeting

    where n is number of observations and IQR is the interquartile range of data.

@@

>>>>

    where n is number of observations and $IQR(x)$ is the inter-quartile range of data.

@@

    The objective is finding an optimal aggregate model which falls in the span of spectrum from a fine-grid model
    to a rigid aggregate model.
    Our presented method calculates a discretization policy for which we calculate a feasible value function.
    Return of a policy shows the quality of the gauged policy.
    Hence, by calculating the accumulative return (eq.\ref{eq:return}) over run of the \textit{true} model and in a
    comparison with the original return we can measure the improvement.

    \begin{equation}
        R = \sum_{k=0}^{\infty} \gamma^{k} r_{k+1}. \label{eq:return}
    \end{equation}
